---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fuzzysys: Simple Fuzzy Inference and Fuzzy Systems

The goal of fuzzysys is to provide a wrapper for fuzzy set functions from the package ['sets'](https://cran.r-project.org/web/packages/sets/index.html). 

fuzzysys re-imagines fuzzy set and inference functions from the original `sets` package by David Meyer et al.<sup>[1](#citation)</sup>, with added customizability and control. It aims to be highly customizable for a variety of needs, without the clutter that comes with more hefty packages.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```


## Another example 

This is a basic example which shows you how to solve a common problem:

```{r example2}
## basic example code
```




<a name="citation">1</a>: Meyer D and Hornik K (2009). “Generalized and Customizable Sets in R.” Journal of Statistical Software, 31(2), pp. 1–27. doi: 10.18637/jss.v031.i02.
