---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fuzzysys: Simple Fuzzy Inference and Fuzzy Systems

fuzzysys is, in some ways, a wrapper package for fuzzy set functions from the package 'sets'. The goal of fuzzysys is to re-imagine fuzzy set and inference functions from the [original `sets` package](https://cran.r-project.org/web/packages/sets/index.html) by David Meyer et al., with more customizability and control. 

fuzzysys compiles useful tools to build a simple fuzzy rule-based expert system model. It aims to be highly customizable for a variety of needs, without the clutter that comes with more hefty packages.

Meyer D and Hornik K (2009). “Generalized and Customizable Sets in R.” Journal of Statistical Software, 31(2), pp. 1–27. doi: 10.18637/jss.v031.i02.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
