---
title: "Using the `fuzzysys` package"
author: "Patricia T. Angkiriwang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `fuzzysys` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Fuzzy logic operators (i.e. negation ("NOT"), conjunction ("AND"), and disjunction ("OR")) can be defined slightly differently depending on which fuzzy logic family or convention one chooses to use. 

With the `sets` package, you would normally have to stick to one so-called fuzzy logic family. For example...

```{r example_sets}
library(sets)

# Define example numeric vectors x and y
x <- c(0.7, 0.8, 0.9)
y <- c(0.2, 0.3, 0.4)

sets::fuzzy_logic("Zadeh") # specifies fuzzy logic family as "Zadeh"

sets::.N.(x) # apply negation
sets::.T.(x, y) # conjunction
sets::.S.(x, y) # disjunction
```

To switch families, one would have to change the default/ current settings, like so: 

```{r example_sets2}
sets::fuzzy_logic("product") # switch fuzzy logic family

sets::.N.(x)
sets::.T.(x, y)
sets::.S.(x, y)
```

Why restrict yourself to only one family, or have an extra line every time you want to switch?!

The wrapper functions defined in this new `fuzzysys` package allow you to specify which family/ type of operator you want to use more concretely, without having to define one single fuzzy logic family.

Let's load the package:

```{r}
library(fuzzysys)
```


Now you can use different versions of the conjunction operator (specified by an argument to.T()) one line after another:

```{r example}
.T(x,y,type="Zadeh")
.T(x,y,type="product")
.T(x,y,type="Fodor")
```

Similarly, for the disjunction operator:

```{r}
.S(x,y,type="Zadeh")
.S(x,y,type="product")
.S(x,y,type="Fodor")
```

And the negation operator (.N.()), which in most fuzzy logic families is defined as $1-x$.

```{r}
x
.N(x,type="Zadeh")
.N(x,type="product")
.N(x,type="Fodor")
```

It's `purrr` friendly, too!

First load the `purrr` package

```{r}
library(purrr)
x_list <- list((1:10)/10, 0.5, 0.7)
y_list <- list((10:1)/10, 0.5, 0.7)
```

Both `sets` and `fuzzysys` can handle one fuzzy logic family (default: "Zadeh") while looping over our 2 lists

```{r}
# with original `sets` wrapper functions
map2(x_list,y_list,sets::.T.)
# with `fuzzysys` wrapper functions
map2(x_list,y_list,.T)
```

But with `fuzzysys` it's easy to switch between families when we use pmap()! Here, three different fuzzy logic families are used: 

```{r}
pmap(list(x_list,y_list,list("Zadeh","product","Fodor")),~.T(..1,..2,type=..3))
```

More information about each fuzzy logic family and their respective operator definitions can be found in the original `sets` [documentation](https://www.rdocumentation.org/packages/sets/versions/1.0-18/topics/fuzzy).

Meyer D and Hornik K (2009). “Generalized and Customizable Sets in R.” Journal of Statistical Software, 31(2), pp. 1–27. doi: [10.18637/jss.v031.i02](https://www.jstatsoft.org/article/view/v031i02).

